### 2018-05-28 README.Rmd
update badge size
fix typo
update graphics

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "tools/README-"
)
```

# pdp <img src="tools/pdp-logo.png" align="right" width="120" height="139" />

@@

@@

As a second example, we'll fit an SVM to the Pima Indians diabetes data included with the package (see `?pima` for details). Note that for some fitted model objects (e.g., `"ksvm"` objects) it is necessary to supply the original training data via the `train` argument in the call to `partial`.

```{r example-svm, fig.width=8, fig.height=4, message=FALSE}
# Fit an SVM to the Pima Indians diabetes data
library(kernlab)  # install.packages("kernlab")
data (pima)  # load the Pima Indians diabetes data
pima.svm <- ksvm(diabetes ~ ., data = pima, type = "C-svc", kernel = "rbfdot",
                 C = 0.5, prob.model = TRUE)

>>>>

```{r, echo = FALSE}
knitr::opts_chunk$set(
  cache = TRUE,
  collapse = TRUE,
  comment = "#>",
  fig.align = "center",
  fig.path = "tools/README-"
)
```

# pdp <img src="tools/pdp-logo.png" align="right" width="130" height="150" />

@@

You can also plot the output directly from `partial()` (although, this is typically not recommended; see the [above-mentioned paper](https://journal.r-project.org/archive/2017/RJ-2017-016/index.html) for details):
```{r example-rf-2, fig.width=7, fig.height=5, message=FALSE}
partial(boston.rf, pred.var = c("lstat", "rm"), chull = TRUE, plot = TRUE,
        plot.engine = "ggplot2", palette = "magma", alpha = 0.9,
        contour = TRUE, contour.color = "white")
```

@@

As a second example, we'll fit an SVM to the Pima Indians diabetes data included with the package (see `?pima` for details). Note that for some fitted model objects (e.g., `"ksvm"` objects) it is necessary to supply the original training data via the `train` argument in the call to `partial()`.

```{r example-svm, fig.width=8, fig.height=4, message=TRUE}
# Fit an SVM to the Pima Indians diabetes data
library(kernlab)  # install.packages("kernlab")
data (pima)  # load the Pima Indians diabetes data
pima.svm <- ksvm(diabetes ~ ., data = pima, type = "C-svc", kernel = "rbfdot",
                 C = 0.5, prob.model = TRUE)
